Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-07 paper_latex_edit - Copy.tex
Sorting-referencing-in-my-paper

	\bibitem{abk}
	Z. Liu, M. Rosario, Z. Ding. "A Markovian Model-Driven Deep Learning Framework for Massive MIMO CSI Feedback," in IEEE Transactions on Wireless Communications, vol. 21, no. 2, pp. 1214-1228, 2022

	\bibitem{abl}
	M. Boloursaz Mashhadi, D. Gündüz. "Deep Learning for Massive MIMO Channel State Acquisition and Feedback," in Journal of the Indian Institute of Science, vol. 100, 2020.

@@

	\bibitem{prac2024}
    Z. Lu, Y. Dong, H. He, S. Jin, and G. Y. Li, 
    ``Practical Deployment for Deep Learning-Based CSI Feedback Systems: Generalization Challenges and Enabling Techniques,''
    \emph{IEEE Wireless Communications}, 
    vol. 31, no. 2, pp. 72--79, 
    Apr. 2024, 
    doi: 10.1109/MWC.001.2300223.

	\bibitem{quant2024}
    M. Yin, S. Han, and C. Yang,
    ``Quantization Design for Deep Learning-Based CSI Feedback,''
    \emph{arXiv preprint arXiv:2503.08125},
    Mar. 2024.

	\bibitem{CSICompression2024}
	J.~Chen, W.~J.~Hillery, K.~R.~Mestav, C.~Nuzman, I.~Saniee, and Y.~Xing, 
	``CSI Compression for Massive MIMO: Model-Based or Data-Driven?,'' 
	\emph{IEEE Wireless Communications}, vol.~32, no.~1, pp.~22--27, Feb. 2025,

	\bibitem{ji2021clnet}
	S. Ji and M. Li, ``CLNet: Complex input lightweight neural network designed for massive MIMO CSI feedback,'' \textit{IEEE Wireless Commun. Lett.}, vol. 10, no. 10, pp. 2318--2322, Oct. 2021

@@

@@

	\bibitem{aby}
	Chakma, A., et al. "Deep Decoder CsiNet for FDD Massive MIMO System," in IEEE Wireless Communications Letters, vol. 12, no. 12, pp. 2073-2077, 2023

@@

	\bibitem{bbb1}
	Markus Nagel, et al. "A White Paper on Neural Network Quantization," in ArXiv, vol. abs/2106.08295, 2021.

@@

	\bibitem{dynamicquantization}
	Y. Zhou, S. Liu, J. Wang, Y. Eiss, X. Huang, and E. Elsen, "Efficient 8-bit quantization of Transformer neural machine language translation model," arXiv preprint arXiv:2006.16669, 2020.

\end{thebibliography}

>>>>

    \bibitem{abk} 
    Z. Liu, M. Rosario, Z. Ding. "A Markovian Model-Driven Deep Learning Framework for Massive MIMO CSI Feedback," in IEEE Transactions on Wireless Communications, vol. 21, no. 2, pp. 1214-1228, 2022.

@@

@@

    \bibitem{prac2024} 
    Z. Lu, Y. Dong, H. He, S. Jin, and G. Y. Li, ``Practical Deployment for Deep Learning-Based CSI Feedback Systems: Generalization Challenges and Enabling Techniques,'' \textit{IEEE Wireless Communications}, vol. 31, no. 2, pp. 72--79, Apr. 2024, doi: 10.1109/MWC.001.2300223.

    \bibitem{quant2024} 
    M. Yin, S. Han, and C. Yang, ``Quantization Design for Deep Learning-Based CSI Feedback,'' \textit{arXiv preprint arXiv:2503.08125}, Mar. 2024.

    \bibitem{CSICompression2024} 
    J.~Chen, W.~J.~Hillery, K.~R.~Mestav, C.~Nuzman, I.~Saniee, and Y.~Xing, ``CSI Compression for Massive MIMO: Model-Based or Data-Driven?,'' \emph{IEEE Wireless Communications}, vol.~32, no.~1, pp.~22--27, Feb. 2025.

@@

    \bibitem{ji2021clnet} 
    S. Ji and M. Li, ``CLNet: Complex input lightweight neural network designed for massive MIMO CSI feedback,'' \textit{IEEE Wireless Commun. Lett.}, vol. 10, no. 10, pp. 2318--2322, Oct. 2021.

    \bibitem{aby} 
    Chakma, A., et al. "Deep Decoder CsiNet for FDD Massive MIMO System," in IEEE Wireless Communications Letters, vol. 12, no. 12, pp. 2073-2077, 2023.

@@

@@

    \bibitem{dynamicquantization} 
    Y. Zhou, S. Liu, J. Wang, Y. Eiss, X. Huang, and E. Elsen, "Efficient 8-bit quantization of Transformer neural machine language translation model," arXiv preprint arXiv:2006.16669, 2020.
\end{thebibliography}
